\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
%\usepackage[empty]{fullpage}
\usepackage[margin=1in]{geometry} %instead of above command
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{cite}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeParagraph}[1]{
    \begin{itemize}[leftmargin=0.2in, rightmargin=0.4in, label={}]
      \small{\item{{#1}}}
    \end{itemize}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kennedy Caisley} \\ \vspace{1pt}
    \small +49 163 1507498 $|$ \href{mailto:kcaisley@uni-bonn.de}{\underline{kcaisley@uni-bonn.de}}
    $|$ \href{www.kennedycaisley.com}{\underline{www.kennedycaisley.com}}
\end{center}

%-----------EXPERIENCE-----------
\section{Appointments}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Graduate Research Associate}{Aug. 2022 -- Present}
    {Univeristy of Bonn}{Bonn, Germany}
    \resumeParagraph{
    Design of mixed-signal blocks (PLL, TDC, AFE) in 28 nm \& 65 nm for detector readout ICs.
    Emphasis on design automation using open source packages (Python \& C++).
    Installation and management of PDK data and ASIC, TCAD, PCB, and FPGA design tools (Cadence, Mentor, Synopsys, Xilinx).
    Administration of IT infrastructure (Fedora \& CentOS) including NFS file servers, LDAP user accounts, and EDA license servers.
    }
  
  \resumeSubheading
    {ASIC Design Intern}{May 2021 -- Dec. 2022}
    {Lawrence Berkeley National Laboratory}{Berkeley, CA, United States}
    \resumeParagraph{
    Designed a radiation-hard monolithic test bench for characterizing charge-sensitive analog front ends in 28 nm bulk CMOS.
    Test bench includes a programmable charge-injection circuit and 10 ps RMS precision time-to-digital converter.
    Top-level chip assembled as system with 28 channels, verified with Calibre DRC/LVS.
    Full-custom design, including a set of logic standard cells and low-power analog cells.
    }

  \resumeSubheading
    {Graduate Research Associate}{Aug. 2019 -- May. 2021}
    {Ohio State University}{Columbus, OH, United States}
    \resumeParagraph{
    Assisted in design, layout, and testing of 65 nm readout IC for pCVD diamond detectors, for use in Beam Conditions Monitor (BCM) of ATLAS experiment at CERN.  
    Designed differential time-over-threshold circuit. Characterized effect of detector capacitance on noise in front-end charge sensitive amplifier.
    Integrated multiple circuit blocks and performed top-level verification of analog subsystem using Calibre DRC/LVS.
    }

  \resumeSubheading
    {Hardware Engineering Intern}{Oct. 2018 -- May 2019}
    {Schweitzer Engineering Laboratories, Inc.}{Pullman, WA, United States}
    \resumeParagraph{
    Designed board-level industrial communications equipment for use in high-noise and high-radiation environments.
    Contributed circuit designs including zero-crossing detectors, switching power supplies, ESD protection, and drivers for off-board coaxial and twisted-pair links.
    Performed passive component tolerance analyses, trace impedance analyses/simulations, and EMC testing (emissions and susceptibility).
    }

  \resumeSubheading
    {System Modeling Intern}{Jun. 2017 -- Aug. 2017}
    {ISO New England, Inc.}{Holyoke, MA, United States}
    \resumeParagraph{
    Developed models for Newton-Raphson numerical analysis of the New England power grid, in Python.
    Conducted power-flow studies for long-term load forecasting, examined impact of no-fault and breaker-open contingencies, and wrote scripts to automate reporting.
    }

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeParagraph{M. Mansour, S. Smith, H. Kagan, \textbf{K. Caisley}, B. Tar; A. Naguib; A. Gorišek; B. Hiti; M. Mali, M. Mikuž, et al. A Fast, Low Jitter, and Low Time-Walk Multi-Channel Front-End IC for Diamond and Silicon Radiation Detectors. \textit{IEEE Transactions on Nuclear Science}. 2023. DOI: \href{https://doi.org/10.1109/tns.2023.3283220}{\underline{10.1109/TNS.2023.3283220}}.
  }

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

  \resumeSubheading
    {University of Bonn}{Aug. 2022 -- In Progress}
    {PhD in Physics}{Bonn, Germany}
    \vspace{5pt}

  \resumeSubheading
    {Ohio State University}{Aug. 2019 -- Jan. 2022}
    {Master's in Electrical Engineering}{Columbus, OH, United States}
    \vspace{5pt}

  \resumeSubheading
    {University of Idaho}{Aug. 2015 -- May 2019}
    {Bachelor's in Electrical Engineering}{Moscow, ID, United States}
    \vspace{5pt}

  \resumeSubHeadingListEnd

\end{document}
