\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeParagraph}[1]{
    \begin{itemize}[leftmargin=0.2in, rightmargin=0.4in, label={}]
      \small{\item{{#1}}}
    \end{itemize}
}

\newcommand{\resumeParagraphAlt}[1]{
    \begin{itemize}[leftmargin=0.2in, rightmargin=0.4in, label={}]
      \small{\item{{#1}}}
    \end{itemize}\vspace{-7pt}
}



\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumePubs}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Lise Minaud} \\ \vspace{8pt}
    \small +33(0)641682417 $|$ \href{mailto:lise.minaud@gmail.com}{\underline{lise.minaud@gmail.com}}
$|$ \href{https://www.linkedin.com/in/lise-minaud-0a8524188}{\underline{linkedin.com/in/lise-minaud}}
\end{center}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master's of Bioinformatics \& Biostatistics}{Sep. 2018 -- Sep. 2020}
      {Université Paris-Saclay}{Orsay, France}

    \resumeParagraph{ \underline{Coursework}: Biological Image Analysis, Biological Dynamic Systems, Database Optimization, Comparative Genomics, Next Generation Sequencing, Bio-statistics, Epidemiology, RNA Bioinformatics, Web Programming}

    \resumeSubheading
      {Bachelor's of Biology}{Sep. 2015 -- Jul. 2018}
      {Sorbonne Université}{Paris, France}

    \resumeParagraph{ \underline{Coursework}: Molecular Biology, Biochemistry, Cellular Biology and Development, Genetic, Physiology of Neuronal and Hormonal Signaling, Model Organisms in Developmental Biology, Ethology and Sociobiology}

    \resumeSubheading
      {Bachelor's of Law}{Sep. 2015 -- Jul. 2018}
      {Université Panthéon-Assas}{Paris, France}
      
   \resumeSubheading
      {Erasmus Exchange}{Sep. 2017 -- Jun. 2018}
      {Charles University}{Prague, Czechia}
      
  \resumeSubHeadingListEnd
  
\section{Research Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
	{Data Scientist}{Apr. 2020 -- May 2023}
	{Institute for Neurodegenerative Diseases, University of California San Francisco}{San Francisco, USA}
       %\resumeSubheading{Advised by Dr. Michael Keiser - %\href{https://keiserlab.org}{\underline{Keiser lab}}}{}{}{}
      \resumeParagraphAlt{Advised by Dr. Michael Keiser - \href{https://keiserlab.org}{\underline{Keiser lab}}
      }
        \begin{itemize}[topsep=0pt]\small
            \item Trained convolutional neural network (w/ PyTorch) to automate the identification of Cerebral Amyloid Angiopathy vessel subtypes, replicating human expert performance with high precision (AUPRC = 0.88-0.90).
            \item Developed whole slide image processing pipeline for histopathological analysis.
            \item Deployed web application to collect labeled data from neuropathologists (120,000 annotations). 
        \end{itemize}
     %}
          \resumeSubheading
      {Bioinformatic Research Intern}{Jul. 2019 -- Aug. 2019}
      {CEA Institute of Cellular and Molecular Radiobiology}{Fontenay-aux-Roses, France}
      \resumeParagraphAlt{Advised by Dr. Annette Schmitz and Dr. Jan Baijer
      }
      \begin{itemize}[topsep=0pt]\small
            \item Analyzed RNA-seq data from breast cancer patients using Next Generation Sequencing methods.
            \item Extracted SNP biomarkers of radiotherapy patients to discriminate genes associated with radiosensitivity.
            \item Utilized SAMtool and BEDtool packages in R lang.
      \end{itemize}
      %}
   \resumeSubHeadingListEnd 
 
\section{Presentations \& Works}
  \resumeSubHeadingListStart
      \resumePubs
	{21st International Conference on Systems Biology}{Oct. 2022 -- \textit{Berlin, Germany}}
      \resumeParagraph{\textit{Automated detection and regional classification of Cerebral Amyloid Angiopathy in digital whole slide images.} \underline{Lise Minaud}, Daniel R. Wong, Sina Ghandian, Harry V. Vinters et al.}

      \resumePubs
	{Alzheimer's Researchers' Symposium}{Aug. 2022 -- \textit{Stanford University, USA}}
      \resumeParagraph{\textit{Automated detection and regional classification of Cerebral Amyloid Angiopathy in digital whole slide images.} \underline{Lise Minaud}, Daniel R. Wong, Sina Ghandian, Harry V. Vinters et al.}

      \resumePubs
	{97th American Association of Neuropathologists Meeting}{Jun. 2021 -- \textit{St. Louis, USA (Remote)}}
      \resumeParagraph{\textit{Automated Detection of Cerebral Amyloid Angiopathy in Amyloid Beta Stained Slides Using Trained Machine Learning Models.} \underline{Lise Minaud}, Daniel R. Wong, Harry V. Vinters et al. \href{https://academic.oup.com/jnen/article/80/6/558/6292307}{\underline{https://doi.org/10.1093/jnen/nlab042}}}


%      \resumePubs
%	{CZI Neurodegeneration Chal. Network Ann. Meeting}{Jun. 2021 -- \textit{San Francisco, USA (Remote)}}
%      \resumeParagraph{\textit{Automated detection and regional classification of Cerebral Amyloid Angiopathy in digital whole slide images.} \underline{Lise Minaud}, Daniel R. Wong, Harry V. Vinters et al.}
  \resumeSubHeadingListEnd


  \section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Tools}{: Python (PyTorch, scikit-learn, OpenCV, NumPy, pandas), R, Git, Linux/Unix Shell} \\ \vspace{5pt}
     \textbf{Spoken Languages}{: French (Native), English (Fluent), Spanish (B2)} \\
    }}
 \end{itemize}

\end{document}